Using Visual Analytics to Explain\\[1ex] Black-Box Machine Learning

### 2018-03-25 tex/introduction/usecase.tex
use case

However, when it comes \todo{}

* Doctor decision tree (doctor note, limitations, residents vs. attending intuition; seniors might not be able to fully explain decisions made because of learned examples)
* inconsistent coding NDC, IDC, hierarchies

>>>>

When it comes to symptoms, doctors often have to weigh different plausible diagnoses against each other, as the same symptoms can appear from different causes.
This is called \emph{differential diagnosis}.
In order to determine which diagnosis has the highest likelihood, Bayesian reasoning is applied.
That is, the conditional probabilities of symptoms with respect to different diagnoses are compared to each other.
The probabilities are determined through historical records.
However, the resulting rules are often simplified to be memorizable by humans.
\todo{cite The Digital Doctor; Robert Wachter; Chapter 9}

While residents (recent medical doctorate graduates) follow those rules religiously, attending physicians (more senior medical doctors) might sometimes follow their intuition, acquired through years of patient interactions.
Thus, such a medical decision might not be fully explainable through empirical statistics alone anymore.
This is equivalent to, for example, a Deep Neural Network that learned some transformations through its hidden layers that lead to hard to interpret interactions of the initial input features.
